\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%     Introduction   %%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Preliminaries}\label{00Sec:Preliminaries}
\addcontentsline{toc}{section}{Preliminaries}

% \renewcommand{\thesubsection}{\MakeUppercase{\romannumeral\value{subsection}}}
\renewcommand{\thesubsection}{\roman{subsection}}
\subsection{Project overviewls}\label{01Sub:ProjectOverview}

The purpose of this project was to develop a firmware solution as part of a job interview for the 
position of Firmware Engineer at Tractian. The project involved designing and implementing hardware
and firmware for data transmissions through a wireless protocol. For this task, the WiFi protocol was
chosen. Although it wasn't necessary, it was added to the project the capability of data collection, so there was
actual information to be sent later. The device was equipped with a temperature sensor to capture data, which was then
stored in a flash EEPROM memory.


\subsection{Project objectives}\label{01Sub:ProjectObjectives}


The main objective of this project is to demonstrate the capabilities of a battery-powered device by successfully
transmitting a 500kB file across a challenging 100-meter open-air gap. This task requires efficient wireless communication
and optimized power management to ensure reliable and uninterrupted data transmission. By accomplishing this objective,
the project aims to showcase the device's ability to overcome distance limitations and deliver data wirelessly, even in challenging
environments.





%%%%%%%%%%%     FIM      %%%%%%%%%%%  
%%%%%%%%     Introduction   %%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\thesubsection}{\arabic{subsection}}


